---
title: "Assignment 4"
format: html
editor: visual
---

# Data Preparation

General questions for office hours: Should we be doing all of our coding in the index.qmd file, or in a separate file?

```{r}
library(tidyverse)
library(readxl)
library(lubridate)
library(ggplot2)
library(ggrepel)
library(janitor)

inadmissibles_2014 <- read_excel("cy_2014_ofo_inadmissibles_redacted.xlsx")

inadmissibles_2014 <-
  clean_names(inadmissibles_2014) |>
  filter(is.na(duplicate_subject_indicator)) |>
  mutate(event_created_datetime = ymd_hms(event_created_datetime)) |>
  mutate(month = month(event_created_datetime)) |>
  mutate(month_name = month(event_created_datetime, label = TRUE, abbr = FALSE))

glimpse(inadmissibles_2014)

```

# Graph 1

Questions about this graph for office hours: For the number labels on each bubble - can they ?

```{r}
inadmissibles_2014 |>
  count(citizenship_country_name) |>
  arrange(desc(n)) |>
  mutate(country_rank = row_number()) |>
  right_join(inadmissibles_2014, by = "citizenship_country_name") |>
  filter(country_rank <= 10) |>
  group_by(citizenship_country_name, mode_of_transport) |>
  mutate(crossings = n()) |>
  ungroup() |>
  ggplot(mapping=aes(x = fct_infreq(citizenship_country_name), y = mode_of_transport)) +
  geom_count(mapping = aes(size = crossings, color = mode_of_transport)) +
  geom_text(mapping = aes(label = crossings), vjust = -2.6, size = 3.3) +
  scale_size_area(max_size = 15) + 
  theme(axis.text.x = element_text(angle = 45, vjust = .85)) + 
  labs(x = "Country", y = "Mode of Transport", color = "Mode of Transport", size = "Number of Crossings", title = "Counts of Unauthorized Border Crossings by Country of Origin and\nMode of Transport") 

```

# Graph 2

Questions about this graph for office hours: Should we get rid of the rows that are causing the warning? Or just suppress the warning?

```{r}
inadmissibles_2014 |>
  count(citizenship_country_name) |>
  arrange(desc(n)) |>
  mutate(country_rank = row_number()) |>
  right_join(inadmissibles_2014, by = "citizenship_country_name") |>
  filter(country_rank <= 10) |>
  ggplot() +
  geom_boxplot(mapping = aes(x = fct_infreq(citizenship_country_name), y = age_at_event_creation_time)) +
  labs(x = "Country of origin", y = "Age", title = "Age distributions by country of origin") +
  theme(axis.text.x = element_text(angle = 45))

```

# Graph 3

Questions for office hours: Can I make these a bit wider? It's very condensed right now

```{r}

inadmissibles_2014 |>
  count(citizenship_country_name) |>
  arrange(desc(n)) |>
  mutate(country_rank = row_number()) |>
  right_join(inadmissibles_2014, by = "citizenship_country_name") |>
  filter(country_rank <= 5, month != "NA") |>
  group_by(month, citizenship_country_name, mode_of_transport) |>
  mutate(crossings = n()) |>
  ungroup() |>
  ggplot(mapping = aes(x = month_name, y = crossings, color = fct_infreq(citizenship_country_name), group = citizenship_country_name)) +
  geom_line() +
  geom_point(mapping = aes(shape = fct_infreq(citizenship_country_name))) +
  scale_y_log10() +
  facet_wrap(~mode_of_transport) +
  labs(x = "Month", y = "Number of Crossings", title = "Unauthorized Border Crossings by Month, Country, and Mode of Transport", color = "Country of Origin", shape = "Country of Origin") +
  theme(axis.text.x = element_text(angle = 45))


```

# Graph 4

```{r}


```
